---
title: "Final"
author: "Eva Portillo Molina"
format: 
  html:
    theme: sketchy
---

***Information about the data***

This is a dataset of movies with "summer" in their title originating from the Internet Movie Database and can be accessed at this link: <https://github.com/rfordatascience/tidytuesday/blob/master/data/2024/2024-07-30/readme.md> .

All variables in the dataset were loaded, but the only variables used in this analysis include the:

-   title_type variable which refers to the type/format of the title (movie, video, or tvMovie)

-   runtime_minutes variable refers to the primary runtime of the title, in minutes

-   genres variable includes up to three genres associated with the title

-   average_rating variable includes weighted average of all the individual user ratings on IMDb

-   num_votes variable refers to number of votes the title has received on IMDb (titles with fewer than 10 votes were not included in this dataset)

```{r, include=FALSE}
#Loading in the data
#| echo: false

library(readr)
library(tidyverse)
library(here)
library(gtsummary)

summer_movies <- read_csv(here::here("data","summer_movies.csv"))

```

## Creating a summary table

```{r}
#| label: tbl-one
#| tbl-cap: "This is my first table"

tble1 <- tbl_summary(
	summer_movies,
	by= title_type,
	include = c(title_type, genres, runtime_minutes, average_rating, num_votes),
	label = list(
		genres ~ "Genres",
		average_rating ~ "Average Rating",
		num_votes ~ "Number of Votes",
		runtime_minutes ~ "Run Time Minutes"
	),
	missing_text = "Missing") |>
	add_overall(col_label = "**Total**") |>
	bold_labels() |>
	modify_header(label = "**Variable**")
tble1

```

@tbl-one shows the descriptive statistics

The median (IQR) number of votes for Comedy movies with a "Movie" type/format title is `r inline_text(tble1, variable = "genres", level = "Comedy", column = "video")`

## Finding the average run time for movies

```{r}
Avg_Runtime <- mean(summer_movies$runtime_minutes, na.rm = TRUE)

```

The average run time for movies is `r Avg_Runtime`

The average run time for movies is `r mean(summer_movies$runtime_minutes, na.rm = TRUE)`

## Running a Regression

```{r }
#| label: tbl-two
#| tbl-cap: Regression table on Number of Votes
library(tidyverse)
library(broom)

tbl_uvregression(
	summer_movies,
	y = num_votes,
	include = c(genres,runtime_minutes, 
							average_rating),
	#did install.packages("broom.helpers")
	method = "lm")

```

@tbl-two is a table regressing the number of votes separately on genres, the movie's run time and the average rating for each movie

## Creating a histogram

```{r}
#| label: "fig-1"
#| fig-cap: "This is my first figure"


# Creating a histogram 
hist(summer_movies$average_rating,
     main = "Distribution of Average Ratings",
     xlab = "Average Rating",
     ylab = "Frequency")

png(filename = here::here("documents", "average_rating_histogram.png"))

hist(summer_movies$average_rating,
     main = "Distribution of Average Ratings",
     xlab = "Average Rating",
     ylab = "Frequency")

dev.off()

#attempting to use broom example
lm <- lm(num_votes ~ runtime_minutes + genres +
							average_rating, data = summer_movies)
tidy_lm<- tidy(lm, conf.int = TRUE)


```

@fig-1 is a histogram on the average rating for movies

```{r, include=FALSE}
#Creating vector of runtime for using function

clean_runtime <- summer_movies$runtime_minutes[!is.na(summer_movies$runtime_minutes)]
clean_runtime
```

Creating a new std. dev function

```{r}


newsd <- function(x){
	n <- length(x)
	mean_val <- sum(x) / n
	stddev <- sqrt(sum((x-mean_val)^2)/(n-1))
	return(stddev)
}


sd <- newsd(clean_runtime)
print(sd) 



```
